### 2021-08-19 plos_latex_template.tex
few edits to MS (JR)

@@

In July 2021, the authors of this article, along with a larger group of people, organized a global and virtual conference for users and developers of the R software, useR!2021. useR! conferences are non-profit conferences organized by volunteers for the community, supported by the R Foundation. Attendees are from the academia and the industry. We aimed at building a high-quality conference in a kind, inclusive, accessible, and welcoming environment for everyone. We would like to share the lessons learned within a year of work organizing this conference, as 10 simple rules towards an inclusive conference. UseR! These rules apply to academic, industry, or mixed conferences; the rules are inspired by a global experience but can also be applied to regional or local conferences.

@@

Conferences are spaces to meet and reconnect with a specific community, learn from the new work in the field and share our own work. The larger the conference, the larger the network and opportunities to meet and learn. However, just like in science and academia in general, conferences can become an exclusive space for a privileged group (e.g. white, male, from a rich country, English-native speaker, with no physical disabilities).

This article aims at suggesting rules for opening conferences towards inclusiveness and diversity, and to truly welcome underrepresented minorities. They are based on the experience of the authors in the organization of a global and virtual conference for users and developers of the R software, useR!2021. We aimed at building a high-quality conference in a kind, inclusive, accessible, and welcoming environment for everyone. [Need a ending sentence to connect to the rules.]

\section*{Rule 1: Embrace all dimensions of diversity}
The first step to be inclusive is to recognize that people are diverse, that some groups face discrimination and might be underrepresented in your community and event. We can make efforts to welcome --and even better, celebrate --all dimensions of human diversity, such as age, body ability, career stage, gender, geographic origin, language, neurodiversity, race, religion, sexual orientation, and socioeconomic background, to name a few. Publishing a diversity statement (e.g. \url{https://user2021.r-project.org/about/diversity_statement/}) and expressing this welcoming spirit in social media will let people know that they are seen, respected and welcome. That this is their space and their community too. 
%ast be aware that participants may come from different backgrounds and that freedom of speech can be used to harm others, so don't let one dimension of diversity (i.e., political opinion) prevail over others. See rule 10.

\section*{Rule 2: Have an inclusive organizing team}
An inclusive conference can only be organized by an inclusive and diverse organizing team. We can invite people from different regions, genders, socioeconomic situations, and other dimensions of diversity. Special attention should be payed to the usually underrepresented groups. If the organization is not used to working with a diverse group, it may be challenging. But the challenges will help the team grow, learn and have more inclusive practices. If the organizing team is global and remote, time zones can be hard to manage, and meetings will end up happening at odd times. The team may also have to review carefully and learn to choose the right words for emails,
social media publications and your website, to be respectful of every culture and situation. 
Team members could be quick to spot text that is not right, or that does not resonate with a particular group of people. An inclusive team will let everyone know if the organization is failing in any aspect of inclusiveness or accessibility, and help improve it.

\section*{Rule 3: Go beyond your limited networks to find the best people for everything}

When inviting people to the organizing team, keynote speakers, program committee, session chairs and others, we should always look for the best in their subject. If there is not much diversity in the first set of names, it does not mean that minorities are not good enough. It probably means that the system has always privileged some groups of people, and that we need to look further to find great people that are not on the spotlight. [At least in one book I've read a discussion about H-index that we could cite here]. Let's look beyond our narrow and often limited networks. And if we start by having an inclusive organizing team (rule 1 or 2), they can help find the right people.

\section*{Rule 4: Have registration rates according to the cost of living of participants}

Conferences, even virtual ones, should have a registration fee mainly for two reasons. The first one is that preparing the conference takes a lot of effort and costs money (e.g. commercial registration tools, captioning, or conference venue if in-person) and it should be reflected on a price. The second reason is that people tend to value more the things they pay for, and there is a higher risk of not showing up to a free even [any publication to back this up?]. On the other hand, if we are aiming for inclusiveness and representation, the socioeconomic context of participants should be taken into account when fixing the registration fees. Usually, there is a higher fee for people from the industry than for academia. We should also consider a lower fee for non-profit organizations, government employees, or free lancers. And use conversion factors for country of residence using data from International Comparison Program report of the World Bank. It is important to include discounts for students as well as for postdocs, as these are often precarious positions. Postdoc status is not always well-defined in academia and can vary for each country, so their payment category should be explicitly defined.

@@

Offering scholarships or grants to attend the conference may be counterproductive, as they can be seen more of a competition and attract people that might not need the money (e.g. their PI could pay for it), but could apply for it to enrich their CV. If the goal is to help the people in need, let's make that clear. Do not give it a fancy name. It is a fee waiver or a discount for the people in need. And the process for applicants should be simplified. People with low resources already have a hard time applying for loans, grants and scholarships in their lives. We should not make their lives harder by asking them to write long paragraphs to convince us that they deserve our support. Many people that cannot afford conferences do not even try to apply for waivers/scholarships because they think it would be hard to get them. We should trust that when they say they need it, it is because they do.

If the conference resources allow it, one could even take a step forwards and offer financial support: child care support, transportation fees (if in-person) or internet connection services (if virtual).

\section*{Rule 6: Make the conference accessible to all}

Conferences are usually inaccessible to people with hearing and visual impairments. They should be taken into account in every stage of the process. Welcoming them into the organizing team would allow them to take part in the decisions since the beginning, and remind us of inaccessible practices that need to improve. In social media communication, images should be accompanied with alternative text and videos with captions. Platforms for conference registration, abstract submission --and, if the conference is virtual or hybrid, chat platforms --should be screen-reader friendly (tested beforehand). Captioning for presentations should be available. If the conference is in-person, presenters should speak to the microphone to make it easier for captioners or interpreters to listen to them. Accessibility guidelines for slides and presentations should be provided to the presenters, and their use should be encouraged. Accessibility means, for example, that the speakers should also provide raw and accessible material to their talks, such as RMarkdown, html or tex files, and that, if they pre-record their presentation, to make sure that their video is shown and their face is visible so that people with hearing impairment can have the possibility to read their lips. Accessibility awards at the end of the conference are a good way to acknowledge the speakers who were mindful of inclusiveness when preparing their talks. Please find an example of accessibility guidelines at \url{https://user2021.r-project.org/participation/accessibility/}.

Accessibility practices should not be left for the last minute. They require time and early decision-making. Conversely, inaccessible decisions are hard to undo; e.g. when finding out too late that a venue is inaccessible for wheelchairs in an in-person conference. 
Bear in mind that most accessibility practices are beneficial to everyone. Captions, for instance, are used by non-native speakers and people that access the conference in loud environments. The prior availability of material benefits people with low bandwidth and non-native speakers as well.

\section*{Rule 7: Put more effort in promoting the conference among groups of people who are usually underrepresented}

If some minorities are under represented in the conference, they may not feel part of the community or may not have the financial resources to attend. And effort must be made to promote the conference as welcoming for everyone and supportive for those who do not have the money %ast: or "the credentials" to be there.
For the former, if part of the community has been historically discriminated, one should emphasize that they are particularly welcome in this event, and that the organization will make sure to make it a safe and inclusive environment for them. For the latter, fee waivers, financial support, and the easiness of the process should be advertised. People who are used to applying and getting rejected for scholarships and waivers may find it relieving that the process will be rather supportive in this case.

@@

In-person interaction is priceless; however, it is more expensive for some, even unattainable for others. This is particularly true for global conferences. Global conferences usually take place in high-income countries, making it too expensive and for many people impossible to attend due to immigration requirements. [Share links to news of conference participants denied entry to countries, and maybe some narrating the whole absurd process for visas] Online conferences are more inclusive because there is not need for a visa or a big budget.

Alternatively, a conference could have an in-person and an online component. This could allow for a group of people to physically interact, while providing many others the opportunity to participate. The challenge in this kind of setting would be to make the online component equally relevant as the in-person component, and not just a consolation price to the less privileged in the community.

\section*{Rule 9: Don't let English be a barrier for good quality participation}

In international conferences, English is often the official language. Submissions, presentations, tutorials and workshops are in English. While one official language is extremely helpful to communicate and English is the primary language in scientific communication, opening the conference to other languages could make it less intimidating to people who are not so fluent in English. Excluding them may also mean missing great innovative pieces of work, because of a language barrier. Advertising the conference in several languages, and considering having workshops and presentations in other languages (with or without captions in English) could help overcome this barrier.

\section*{Rule 10: Have a code of conduct team}

To maintain and inclusive and safe space in the conference, there should be a code of conduct and a team to enforce it. `The purpose of a code of conduct is to protect members of a community from harm in that community's spaces. The people who need the protection of a code of conduct are usually those with less power or privilege, as more powerful or privileged people are often already protected from most harm.' (coc book)
The code of conduct should be displayed prominently in several spaces of the conference to deter people from incurring in unaccepted behavior.

The code of conduct team should receive training to have a clear understanding on what to enforce and what not to enforce in a code of conduct, how to receive reports, respond to incidents, and communicate the responses. A diverse code of conduct team could be more understanding of intersectionality issues in discrimination and harassment practices.

@@

The ten rules stated here can be adapted depending on the conference settings. We are aware, from our own experience, that enforcing these rules require a lot of work that is not compensated financially or in promotions. The rewards from this practice can be a healthier, stronger and more inclusive community, empowering people that are historically marginalized, and learning from them, thus increasing the quality of the conference.

\section*{Acknowledgments}
The authors of this piece would like to thank every single member of the organizing team of useR!2021 for their valuable contribution to an inclusive conference experience. And the R Foundation for their support to the conference.

@@

% % Either type in your references using
% % \begin{thebibliography}{}
% % \bibitem{}
% % Text
% % \end{thebibliography}
% %
% % or
% %
% % Compile your BiBTeX database using our plos2015.bst
% % style file and paste the contents of your .bbl file
% % here. See http://journals.plos.org/plosone/s/latex for 
% % step-by-step instructions.
% % % 
% \begin{thebibliography}{10}

>>>>

%strikethrough
\usepackage{soul}

@@

In July 2021, the authors of this article, along with a larger group of people, organized a global and virtual conference for users and developers of the R software, useR! 2021. useR! conferences are strictly non-profit and are organized by volunteers from the R community and supported by the R Foundation. These global meetings include attendees from both academia and the industry. This year, we aimed at building a high-quality conference in a kind, inclusive, accessible, and welcoming environment for everyone. In this article, we share a few critical lessons learned during the past year's work organizing this conference. We highlight these as the 10 simple rules to host an inclusive conference. These rules apply equally to academic, industry, or mixed conferences; the rules are inspired by a global experience but can also be easily adapted and applied to regional or local conferences.

@@

Conferences are spaces to meet and reconnect with members from a specific community, learn about new advances in the field and share our recent contributions. The larger the conference, the larger the opportunities to network and learn from your cohort. However, just like in science and academia in general, conferences can become an exclusive space for privileged groups (e.g., white, male, from a rich country, English-native speaker, with no physical disabilities)  \cite{arend_disparity_2019, timperley_he_2020, gewin_what_2019, brown_ableism_2018}.

Calls to improve diversity in many academic spaces, including conferences, are becoming frequent as communities and scientific societies are called out for overrepresenting specific groups of people. While these systematic issues are beginning to be addressed, there is scope for much improvement all around.

Diversity encompasses multiple dimensions: age, body ability, career stage, gender, gender identity,  geographic origin, language, neurodiversity, race, religion, sexual orientation, and socioeconomic background, to name a few. There are implicit hierarchies along these axes, and some statuses (e.g., being cisgender, white, male, from the US or Europe) hold the privilege of being the default settings for which all systems are consciously and unconsciously built. Thinking about diversity and inclusion is thinking about counteracting the structures that hold these hierarchies in place.

%some groups face discrimination and might be underrepresented in your community and event \cite{timperley_he_2020}

This article suggests rules for pivoting traditional conferences towards inclusiveness and diversity and welcoming minoritized groups. These tips stem from the authors' experience in organizing a global and virtual conference for users and developers of the R programming language, useR! 2021. We aimed at building a high-quality conference not just in terms of technical content but embracing everyone in a kind, inclusive, accessible, and welcoming environment, critical in the context of the COVID-19 pandemic. Most of the authors also have experience organizing other regional and national academic conferences and events in communities of practice such as R-Ladies and The Carpentries. Here, we share the lessons learned within the past year of organizing this global useR conference, summarized as 10 simple rules towards an inclusive conference.

\section*{Rule 1: Set realistic but bold diversity indicators}
.
As a starting point, identify which groups are usually unsupported or discriminated against in the community or event of interest, and determine the contributing factors. Next, set measurable indicators of success when organizing a diverse conference. The numbers resulting from these indicators are not the primary goal, and this is not about performative allyship. Instead, these numbers should guide and help hold the organizing team accountable towards these diverse and inclusive goals.

We found it greatly helpful to publish a diversity statement (e.g., \url{https://user2021.r-project.org/about/diversity_statement/}) and express this welcoming spirit in your communication strategy (social networks, website, brand, and visual identity) and in every decision you make, will let people know that they are seen, respected, and welcomed, and that this is their space and community too. However, it is important to not stop with a statement alone, but identify specific goals and tasks that ensure compliance with these larger goals, for e.g., identifying accessible platforms, developing a detailed code of conduct, and accessibility guidelines (see other Rules below).

\section*{Rule 2: Have an inclusive and diverse organizing team}
A genuinely inclusive conference can only be organized by an inclusive and diverse organizing team. Build a team with people from different regions, genders, socioeconomic statuses, and other aspects of diversity. Particular attention should be paid to the usually underrepresented groups (see \textbf{Rule 1} discussing the dimensions of diversity lacking in your community and event). To ensure a deeper understanding of the challenges in different diverse groups, it is essential to create a representative working group that functions as a snapshot of the community at large. Even if creating and maintaining such an interdisciplinary team is challenging, the positive outcomes far outweigh any minor inconveniences, and the team will grow, learn, and embrace more inclusive practices. For instance, if the organizing team is global and remote, time zones can be hard to manage, with meetings scheduled at odd hours. The team may also have to review carefully and teach themselves the correct vocabulary for internal and external communication and identify the best platforms to mechanisms to account for every culture and situation. 
A successful well-oiled inclusive team will provide a safe space for everyone not just to learn and grow but identify critical aspects that are working or failing to improve inclusiveness and accessibility together \cite{hong_groups_2004}.

%rj: Yani's refs to have just in case:
%https://sites.lsa.umich.edu/scottepage/wp-content/uploads/sites/344/2015/11/pnas.pdf; https://www.pnas.org/content/early/2014/11/13/1407301111; https://www.mckinsey.com/business-functions/organization/our-insights/why-diversity-matters

\section*{Rule 3: Finding the best people for each task}

While this rule may seem intuitive, one would be surprised by how often conference organizers tend to do everything themselves instead of reaching out to the right people for the right task -- likely because the latter involves careful planning and communication well ahead of time or because they naively overestimate their expertise in areas they lack practical experience in. For e.g., a cisgender or non-neurodiverse person estimating what might work best for the LGBTQ+ or people with hearing and seeing difficulty. 
Therefore, to build your team of organizers for the conference, you need to actively seek out and recruit the best people for each task, akin to filling your team with the best, diversified portfolio. However, the intention to put together a diverse team alone is not enough. One needs to look for, reach out to, invite, encourage, and onboard these people until there is ample representation across the diversity spectrum and dimensions [\textbf{Fig. 1}]. To achieve this, it will be necessary to go beyond one's limited networks when inviting people to the organizing team, keynote speakers, program committee, session chairs, reviewers, and others. Ensuring diversity in each of these teams and panels is a deliberate process -- if there is not much diversity in the first set of names, it needs to be revised to include people from minoritized groups. If these groups aren't showing up in the A-list, it is seldom because of their technical acumen -- it is because we, as organizers, are not used to turning every work and looking in unfamiliar places to bring in the talent.  Many of our biased lists are products of the existing systems that have always privileged some groups of people \cite{dwyer_notice_2021, sarabipour_evaluating_2020}, thus encouraging us to look further to find great people that are not routinely in the spotlight. We need to go beyond our narrow and often limited networks. So, as long as we start with an inclusive and diverse organizing team (\textbf{Rule 2}), we can aim at finding the right people for various aspects of the conference organization. The regional and local communities are also good sources to tap into. For example, for useR! 2021, groups like AfricaR, R-Ladies, MiR, R Forwards, and LatinR were fundamental to reach people for the organizing team, potential attendees, and sponsors.

\section*{Rule 4: Set registration rates commensurate with the registrant's cost of living}

Conferences, even virtual ones, should have registration fees for two primary reasons. The first one is that preparing the conference involves a lot of concerted effort and costs money (e.g., commercial registration tools, captioning, or conference venue, if in-person) and this translates to the participation fee. The second reason has to do with the human psychology -- people value more the things they pay for, and there is a lower attendance rate for free events with registration /cite{eventbrite_ultimate_2017}[any publication to back this up?]. On the other hand, if we are aiming for inclusiveness and representation, the socioeconomic context of participants should be taken into account when determining the registration rates. Usually, there is a higher fee for people from the industry than for academia (~ proportionate to income). We should also consider a lower fee for non-profit organizations, government employees, or freelancers, and use conversion factors (for country of residence using data from International Comparison Program report of the World Bank \cite{arend_disparity_2019}). It is important to include discounts for students as well as for postdocs (early career trainees) to encourage their participation \cite{sarabipour_evaluating_2020, andalib_postdoc_2018, kaplan_postdoc_2012}. Since postdoc (or trainee) statuses are not always well-defined in academia and can vary for each country, their payment category should be explicitly defined. Disabilities may also increase the overall cost of conferences, especially in-person \cite{de_picker_rethinking_2020, irish_increasing_2020}; discounts would help reduce the financial burden for these factions too.

Representation is an important aspect of diversity and inclusivity: see people like you, from your country, that speak your language is one of the best way to feel you belong, this is way the rates can not only being different for registration, but also, for sponsors, this allows us to have institutions and companies from all over the world being part of the conference which also means they will communicate about our event in their local communities.

@@

Offering scholarships or grants to attend the conference may be counterproductive, as they can be seen as more of a competition and attract people that might not need the money (e.g., when their PI could pay for it) but could apply for it to enrich their CV while filtering out people who do not feel entitled to earn them. If the goal is to help the people in need, the language needs to make that clear without shrouding it with fancy-sounding phrases. Ultimately, it is a fee waiver or a discount for the people who need additional financial support. Also, the process for applicants should be simplified. People with limited resources already have a hard time applying for loans, grants, and scholarships all their lives. We should not make the attendees' lives more challenging by asking for long essays to convince us that they deserve our support. \st{Many people that cannot afford international conferences do not even try to apply for waivers/scholarships because they are discouraged by the requirements, the process, and partly because they believe it would be hard for them to win financial/travel aid.} For this stage of the process, a certain degree of trust goes a long way -- when they say they need the support, it is best to give them the waiver rather than second guess their eligibility. Also, the participant metadata (e.g., demographics, gender, career stage) is already a strong indicator of their potential need for aid.
If the conference resources allow it, the organizers could even take further steps to offer financial support for activities that help them have the time and resources to be at the conference: child care support, transportation fees (if in-person), or internet connection services (if virtual).

\section*{Rule 6: Make the conference accessible to all, from start to end}

Conferences are usually inaccessible to people with hearing, visual, and other disabilities \cite{price_access_2009}. Each of these groups should be considered at every stage of the planning process. Welcoming representatives from these groups into the organizing team would allow them to take part in the decisions from the beginning and spot right away the inaccessible practices that need to improve (see \textbf{Rule 2}). If the conference is in person, the venue must be accessible for people with mobility limitations. A quiet space for neurodivergent people and a space for breastfeeding should also be provided. Images used in communications about the conference should be accompanied by alternative text and videos with captions and sound. Platforms for conference registration, abstract submission -- and chat platforms, if the conference is virtual or hybrid -- should be screen-reader friendly and with low technology requirements (that do not have compatible hardware, software, and internet connection requirements to function, all this tested beforehand). Captioning for presentations should be available in more than one language if possible. If the conference is in-person, presenters should speak into a microphone to make it easier for captioners or interpreters to listen to them. Accessibility guidelines for slides and presentations should be provided to the presenters, and their use should be encouraged (see \url{https://user2021.r-project.org/participation/accessibility/} for example). Among other things, the speakers should provide raw and accessible material to their talks before the conference, e.g., such as RMarkdown, HTML, or TeX files; if they prerecord their presentation, they should include their video and ensure that their face is visible so that deaf and hard-of-hearing people can read their lips if needed. Accessibility awards at the end of the conference are an excellent way to acknowledge the speakers who were mindful of inclusiveness when preparing and delivering their talks.

Accessibility practices are not afterthoughts that can be dealt with at the last minute. They require time and early decision-making \cite{irish_increasing_2020}. Conversely, inaccessible decisions are hard to course-correct, e.g., when finding out too late that a venue is inaccessible for wheelchairs in an in-person conference. 
Bear in mind that most accessibility practices are beneficial to everyone. Captions, for instance, are used by non-native speakers and people that access the conference in loud environments. The prior availability of material benefits people with low bandwidth and non-native speakers as well.

\section*{Rule 7: Take deliberate efforts to promote the conference among underrepresented groups}

If some minoritized groups are underrepresented in the conference, they may not feel like they belong. 
If part of the community has been historically discriminated against, one should emphasize that they are particularly welcome in this event and that the organization will make it a safe and inclusive environment. 
An effort must be made to promote the conference as welcoming and supportive for those without the necessary 'credentials' or resources. For the latter, fee waivers, financial support, and ease of application/registration should be advertised. People who are used to applying and getting rejected for scholarships and waivers may find it relieving that the process will be supportive rather than discriminatory against underrepresented groups. Providing financial and other support (e.g., childcare, flexible hours) will help minoritized groups partake more willingly in the organization and the actual conference.
%ast likewise, some key people in your organizing team might not be able to collaborate without remuneration. Resources permitting, it may be a good idea to secure funds to offer stipends to them.

@@

In-person interaction is priceless; however, it is more expensive for some, even unattainable for others \cite{arend_disparity_2019, timperley_he_2020, niner_better_2021}. This inaccessibility is particularly true for global conferences that usually take place in high-income countries, making it financially demanding for international participants and often impossible to attend due to immigration requirements \cite{sarabipour_evaluating_2020, gewin_what_2019}. Online conferences are more inclusive and do not need a visa or a big budget.

Alternatively, a conference could have a hybrid format with an in-person and online component. This dual format could allow a group of people to interact face-to-face while providing many others the opportunity to participate remotely. The challenge in this kind of setting would be to make the online component equally relevant as the in-person component and not just a consolation prize to the less privileged in the community \cite{niner_better_2021}.

\section*{Rule 9: Don't let language restrict high-quality participation}

In international conferences, English is often the official language. Submissions, presentations, tutorials, and workshops are in English. The platforms, the webpage, and official communications are also in English. While English is the primary language in scientific communication and one official language makes it conducive to communicate widely, opening up the conference to other languages could make it less intimidating to people who are not fluent in English \cite{niner_better_2021}. Excluding them may potentially lead to missing innovative contributions brought about by a language barrier. Advertising the conference in several languages and considering having non-English workshops and presentations (with or without captions in English) could help overcome this barrier. For instance, hosting one international day/session per conference might be a great place to start!

\section*{Rule 10: Have a code of conduct and a team to reinforce it}

To ensure an inclusive, friendly, and safe space in the conference, the organizers need to a clearly define the code of conduct and a team to enforce it \cite{favaro_your_2016}. `The purpose of a code of conduct is to protect members of a community from harm in that community's spaces. The people who need the protection of a code of conduct are usually those with less power or privilege, as more powerful or privileged people are often already protected from most harm.' \cite{aurora_how_2018}
The code of conduct should be displayed prominently in several spaces of the conference to deter people from incurring in unaccepted behavior.

The code of conduct team should receive training to understand unambiguously what to and not to enforce in a code of conduct, how to receive reports, respond to incidents, and communicate their responses. A diverse code of conduct team will be more understanding of intersectionality issues in discrimination and harassment practices.

@@

The ten rules stated here can be adapted depending on the conference format and settings. From our own experience, we are aware that enforcing these rules requires a tremendous amount of work and is not compensated financially or otherwise. However, the rewards from these suggested best practices will provide a healthier, stronger, and more inclusive community, empowering historically marginalized people and learning from them, thereby increasing the overall quality of the conference. Also, since these are early days and accessibility is not as widespread as it should be, the process might seem exacting. Hopefully, if more conferences and domains employ these techniques, the process will get more streamlined, straightforward, and mainstream to adapt with minimal overhead. After all, the strength of any community lies in its ability to be adaptive, inclusive, and accessible.

\section*{Acknowledgments}
The authors of this piece would like to thank every single member of the organizing team of useR! 2021 [insert full list of organizers <LINK>] for their valuable contribution to an inclusive conference experience, and the R Foundation for their financial support for useR! 2021.

@@

% % Either type in your references using
% % \begin{thebibliography}{}
% % \bibitem{}
% % Text
% % \end{thebibliography}
% %
% % or
% %
% % Compile your BiBTeX database using our plos2015.bst
\bibliography{references}
% % style file and paste the contents of your .bbl file
% % here. See http://journals.plos.org/plosone/s/latex for 
% % step-by-step instructions.
% % % 
% \begin{thebibliography}{10}
